`flippant` --- An `R` package for the automated analysis of fluorescence--based

### 2016-12-18 inst/manuscript/manuscript.rmd
Fix a minor typo/formatting issue;

Figure \@ref(fig:figure2-creation) A emphasizes reproducibility between
independent experiments ("Experiment 1" and "Experiment 2") on the four probed
rhodopsins. Forgoing reproducibility analysis in favor of a potentially more
reliable result and following more closely the analysis in Figure 4C--F by
@ploier_dimerization_2016, a single fit may be performed for the combined data
from all experiments as follows, resulting in 
Figure \@ref(fig:figure2-creation)B:

>>>>

Figure \@ref(fig:figure2-creation)A emphasizes reproducibility between
independent experiments ("Experiment 1" and "Experiment 2") on the four probed
rhodopsins. Forgoing reproducibility analysis in favor of a potentially more
reliable result and following more closely the analysis in Figure 4C--F by
@ploier_dimerization_2016, a single fit may be performed for the combined data
from all experiments as follows, resulting in 
Figure \@ref(fig:figure2-creation)B:
